How to run your first Bayesian analysis using jags software in R

### 2022-10-20 text/17/first-jags.Rmd
Updated 17/consulting-trap.md
Standardized tags

---
title: "How to run your first Bayesian analysis using jags software in R"
author: "Steve Simon"
source: "http://blog.pmean.com/first-jags/"
date: "2017-01-28"
category: Blog post
tags: 
- Bayesian statistics
- Incomplete pages
output: html_document
---

@@

Make sure that you have [jags installed][jags1] on your computer as well as the [rjags package][jags2]

>>>>

---
title: "How to run your first Bayesian analysis using jags software in R"
author: "Steve Simon"
source: "http://blog.pmean.com/first-jags/"
date: "2017-01-28"
category: Blog post
tags: 
- Bayesian statistics
- Incomplete page
output: html_document
---

@@

Make sure that you have [jags installed][jags1] on your computer as well as the [rjags package][jags2].
